Testing atlantisom: what if we interpolate the weight at stage output to true age?

### 2019-05-19 InterpolateWeightAtAge.Rmd
interpolation function part1

```{r interpolate-wtage}
# a function to go into atlantisom, sketched here, reuse calc_stage2age as possible
calc_wtTrueage <- function(wtagecl_data, fgs.file) {
  # get number of ages per agecl from fgs.file
  # match species in wtagecl_data to those species in the fgs file
  fgs <- load_fgs(fgs.file)
  species.code <- fgs$Code
  turnedon <- fgs[fgs$IsTurnedOn > 0, ]
  names <- turnedon$Code

  # Figure out the groups that have multiple ages classes in each stage (or
  # cohort)
  multiple_ages <- turnedon[turnedon$NumAgeClassSize>1, c(1,4,10)]
  num_multi_age <- dim(multiple_ages)[1]

  ntimesteps <- length(unique(wtagecl_data$time))

>>>>

```{r interpolate-wtage}
# a function to go into atlantisom, sketched here, reuse calc_stage2age as possible

fgs.dir <- here("atlantisoutput", "NOBACERESGlobalSustainability")
fgs.file <-  "nordic_groups_v04.csv"
wtagecl_data <- wtage_annsurv

calc_wtTrueage <- function(wtagecl_data, fgs.file) {
  # get number of ages per agecl from fgs.file
  fgs <- load_fgs(fgs.dir, fgs.file)
  species.code <- fgs$Code
  turnedon <- fgs[fgs$IsTurnedOn > 0, ]

  # Figure out the groups that have multiple ages classes in each stage (or
  # cohort) this is from the full model
  multiple_ages <- turnedon[turnedon$NumAgeClassSize>1, c(1,4,10)]

  # match species in wtagecl_data to those species in the fgs file
  sppwt <- levels(wtagecl_data$species)
  multiple_ages <- multiple_ages[multiple_ages$Name %in% sppwt, ]

  #now get indices
  names <- multiple_ages$Code
  num_multi_age <- dim(multiple_ages)[1]

  # timesteps from input wt file
  ntimesteps <- length(unique(wtagecl_data$time))
